checkData

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

# Harmonize length limits

@@

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks
         length_harmonized = str_remove(wordLimits, pattern = fixed("YES (copy and paste the limits in the 'other' section below), "))), # remove data entry question text
```

policyData <- policyData %>%
  mutate(wordLimits = str_remove_all(wordLimits, pattern = '"'), #  remove any quotation marks
         wordLimits = str_remove(wordLimits, pattern = fixed('YES (provide number of words/comments below), ')), # remove option text
         wordLimits = case_when(
           wordLimits == 'not more than 1000 words and 2 pages' ~ as.character(2*pageToWord),

# Harmonize PPC names

>>>>

## Harmonize length limits

@@

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks
         length_harmonized = str_remove(length_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         length_harmonized = case_when(
           length_harmonized == "1,000 words" ~ "1000",
           length_harmonized == "1,500 words (one figure and/or one table allowed within word count)" ~ "1500",
           length_harmonized == "1000 words" ~ "1000",
           length_harmonized == "16 pages" ~ as.character(16*pageToWord),
           length_harmonized == "2000 words" ~ "2000",
           length_harmonized == "265 lines of text including references" ~ as.character(265*linesToWord),
           length_harmonized == "3500 words (title page and references included)" ~ "3500",
           length_harmonized == "400 words" ~ "400",
           length_harmonized == "5 pages, including abstract, references, tables, and figures." ~ as.character(5*pageToWord),
           length_harmonized == "500 words" ~ "500",
           length_harmonized == "600-800 words" ~ "800",
           length_harmonized == "750 words" ~ "750",
           length_harmonized == "Approx. 1,000 words" ~ "1000",
           length_harmonized == "approximately 1,000 words" ~ "1000",
           length_harmonized == "as concise as possible, and ideally not exceed 1,200 words" ~ "1200",
           length_harmonized == "at maximum half the length of the target article." ~ "Qualitative",
           length_harmonized == "Maximum length: 1100 words." ~ "1100",
           length_harmonized == "short" ~ "Qualitative",
           length_harmonized == "up to 2,000 words counting 500 words per table and figure" ~ "2000",
           TRUE ~ length_harmonized
         )) 
```

## Harmonize time-to-submit limits

Journals used different units to report time limits (e.g., weeks, months, years). We will convert these various units to weeks using the following approximations.

```{r}
monthToWeek <- 4.35 # number to multiply months by to get weeks
yearToWeek <- 52 # number to multiply years by to get weeks
```

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(time_harmonized = str_remove_all(time, pattern = '"'), #  remove any quotation marks
         time_harmonized = str_remove(time_harmonized, pattern = fixed("YES (provide detail of time limits below), ")),# remove data entry question text
         time_harmonized = case_when(
           time_harmonized == "3 months" ~ as.character(3*monthToWeek),
           time_harmonized == "6 months" ~ as.character(6*monthToWeek),
           time_harmonized == "9 months" ~ as.character(9*monthToWeek),
           time_harmonized == "Draft proposed comments will be due on a tight time- line (i.e., 2– 4 weeks after solicitation), to be determined by the Editor." ~ "4",
           time_harmonized == "he Commentary mechanism is most effective when used to address a contemporary publication" ~ "Qualitative",
           time_harmonized == "Matters Arising articles are interesting and timely scientific or academic comments" ~ "Qualitative",
           time_harmonized == "recent" ~ "Qualitative",
           time_harmonized == "recently published" ~ "Qualitative",
           time_harmonized == "UNCLEAR (provide detail in the 'other' section below), recently published" ~ "Qualitative",
           time_harmonized == "YES (copy and paste the limits in the 'other' section below), 1-year (except for a test of replication)" ~ as.character(1*yearToWeek),
           TRUE ~ time_harmonized
         )) 
```

## Harmonize PPC names
